On the eletrodynamic of moving bodies

### 2019-05-16 Article_AS.Rmd
materiel et methode

```
where RD is the mean ring density (kg∙m-3), CA is cambial age (years), b0, b1 and b2 are empirically determined parameters, and e is the residual error term. Parameter b0 denotes the intercept when CA approaches a theoretical value of 0. We noticed that it was impossible to optimize the equation using the same estimated parameters for all tree cores, because the pattern of variation of annual rings average density of each tree is more or less different from the others. We, therefore, used the optim function of the stats package in the R [@R2018] statistical programming environment to find the best parameters iteratively for each tree core . The fit of the model was evaluated by visual analysis of the model residual curves against adjusted values and explanatory variables, fit indices (R2) (Parresol 1999). The graphic description in figure 1 of the three parameters of our model makes it possible to

>>>>

```
where RD is the mean ring density (kgm-3), CA is cambial age (years), b0, b1 and b2 are empirically determined parameters, and e is the residual error term. Parameter b0 denotes the intercept when CA approaches a theoretical value of 0. We noticed that it was impossible to optimize the equation using the same estimated parameters for all tree cores, because the pattern of variation of annual rings average density of each tree is more or less different from the others. We, therefore, used the optim function of the stats package in the R [@R2018] statistical programming environment to find the best parameters iteratively for each tree core . The fit of the model was evaluated by visual analysis of the model residual curves against adjusted values and explanatory variables, fit indices (R2) (Parresol 1999). The graphic description in figure 1 of the three parameters of our model makes it possible to
